---
title: "Hands On 3: Web Structure Mining"
output: html_notebook
---
### For R beginners
New chunk *Ctrl+Alt+I*

Execute chunk *Ctrl+Shift+Enter*

Execute all chunks *Ctrl+Alt+R*

HTML preview *Ctrl+Shift+K*

# 3.1 Link analysis

```{r}
# Preparations
library(igraph)
```

1. Using the function make_graph(), with directed=F, build the undirected version of the networkin Figure 1 and answer the following questions.

```{r}
gU <- make_graph(c("a","d",
                   "a","f",
                   "b","f",
                   "c","b",
                   "e","f",
                   "f","c",
                   "f","d"),
                 directed = F)
```


```{r}
# a) Plot the obtained graph.
plot(gU)
```

```{r}
# b) Obtain the set of vertices and edges.
V(gU)
E(gU)
```

```{r}
# c) Obtain the adjacency matrix.
gU[]
```

```{r}
# d) Obtain the centrality degree, closeness and betweenness of each node.
degree(gU)
closeness(gU)
betweenness(gU)
```

2. Using the function make_graph(), build the network in Figure 1 and answer the following questions.

```{r}
gD <- make_graph(c("a","d",
                   "a","f",
                   "b","f",
                   "c","b",
                   "e","f",
                   "f","c",
                   "f","d"),
                 directed = T)
```

```{r}
# a) Plot the obtained graph.
plot(gD)
```

```{r}
# b) Obtain the set of vertices and edges.
V(gD)
E(gD)
```

```{r}
# c) Obtain the adjacency matrix.
gD[]
```

```{r}
# d) Obtain the centrality degree, closeness and betweenness of each node.
degree(gD)
closeness(gD)
betweenness(gD)
```

```{r}
# e) Plot the same graph, but with different layouts.
l <- layout_in_circle(gD)
plot(gD,layout=l)

l <- layout_as_star(gD)
plot(gD,layout=l)

l <- layout_as_tree(gD)
plot(gD,layout=l)

plot(gD,layout=layout_nicely(gD))
```

```{r}
# f) Obtain the list of nodes by decreasing order of their hub scores.
hs <- hub_score(gD)
sort(hs$vector, decreasing = T)
```

```{r}
# g) Obtain the list of nodes by decreasing order of their authorities scores.
as <- authority_score(gD)
sort(as$vector, decreasing = T)
```

```{r}
# h) Obtain the list of nodes by decreasing order of their page rank scores with a damping factor of 0.9.
pr <- page_rank(gD, damping=0.9)
sort(pr$vector, decreasing = T)
```

# 3.2 Communities

3. Load the network “Zachary”, which consists of a social network of friendships between 34 members ofa karate club at a US university in the 1970s. Answer the following questions.

```{r}
# Preparation
karate <- make_graph("Zachary")
```


```{r}
# a) Plot the obtained graph.
plot(karate)
```

```{r}
# b) Apply the Girvan-Newman algorithm to detect communities, through the function cluster_edge_betweenness().
ceb <- cluster_edge_betweenness(karate)
ceb
# cef is used more often with high density networks, careful since it uses more computer power
```

```{r}
# c) Plot the result of detected communities over the graph.
plot(ceb,karate)
```


```{r}
# d) What do the functions sizes() and membership() give you?
sizes(ceb)
membership(ceb)
```

```{r}
# e) Plot the result of obtained communities as a hclust object.
plot(as.hclust(ceb))
```

```{r}
# f) Apply one of the modularity maximization techniques to detect communities, through the function cluster_fast_greedy().
cfg <- cluster_fast_greedy(karate)
cfg
# cfg is used more often with large networks
```

```{r}
# g) Explore the obtained results.
plot(cfg, karate)
plot(cfg, karate,
     layout=layout_as_star(karate))

sizes(cfg)
membership(cfg)
hc <- as.hclust(cfg)
plot(hc)

# Displaying the separation between communities
rect.hclust(hc,3)
```

4. Detect and explore the communities obtained by the two above algorithms regarding the network of exercise 1.

```{r}
# Preparing display for two columns 
par(mfrow=c(1,2))

plot(cluster_edge_betweenness(gU), gU,
     main="Edge Betweenness")

plot(cluster_fast_greedy(gU), gU,
     main="Fast Greedy")
```
