---
title: "Hands On 2: Web Usage Mining"
output: html_notebook
---
### For R beginners
New chunk *Ctrl+Alt+I*

Execute chunk *Ctrl+Shift+Enter*

Execute all chunks *Ctrl+Alt+R*

HTML preview *Ctrl+Shift+K*

# 2.1 Simple Recommendation Strategies

```{r}
# Preparations
library(dplyr)
df <- read.csv("~/4year/2semester/dtII/CSVs/log.csv")
View(df)
```

## Most Visited Pages
1. Recommend the 3 most visited pages. For that purpose:

```{r}
# a) inspect how many times each page was visited.
df %>% group_by(PAGE) %>% count()
```

```{r}
# b) sort the pages by decreasing number of visits.
df %>% group_by(PAGE) %>% count() %>% arrange(desc(n))

# different method with tally function that does the same as count and arrange combined
# df %>% group_by(PAGE) %>% tally(sort = TRUE)
```

```{r}
# c) obtain the top 3 pages for recommendation.
# pull() extracts a single column from the data frame and makes it a vector
df %>% group_by(PAGE) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(PAGE)
```

## Using Clustering Results
2. Suppose we want to form two clusters of users, according to the pages they have visited. For that purpose:

```{r}
# a) start by transforming the log access data into a matrix that has on each row a user and for each user the information on his visits to each page; this can be obtained with the table() function.
dat <- table(df$USER, df$PAGE)
dat
```

```{r}
# b) use the function dist() to obtain a distance matrix with the Euclidean distance between the users.
dm <- dist(dat)
dm
```

```{r}
# c) check for alternatives in the help page of dist().
# others "maximun", "manhattan", "minkowski", "jaccard"
```

```{r}
# Package shown by professor in class
library(recommenderlab)
summary(pr_DB)

dm <- dist(dat, method = "jaccard")
```

```{r}
# d) use the function hclust() with the distance matrix to obtain an agglomerative clustering model of this data.
c1 <- hclust(dm)
```

```{r}
# e) visualize the obtained dendogram with function plot().
plot(c1)
```

```{r}
# f) visualize the dendogram again, but now with option hang=-0.1.
plot(c1, hang=-0.1)
```

```{r}
# g) use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user.
cm <- cutree(c1,2)
cm
```

```{r}
# h) use the function rect.hclust() to draw the previous solution in the dendogram.
plot(c1, hang=-0.1)
rect.hclust(c1,2)
```

3. Recommend the top 2 pages for users of cluster 1. For that purpose:

```{r}
# a) inspect what were the pages visited by users in cluster 1.

# with mutate we can add the cluster to each user belongs to the df table
dd <- mutate(df, Cluster=cm[df$USER])
dd

filter(dd,Cluster==1) %>% select(PAGE)
```

```{r}
# b) inspect how many times each of these pages was visited.
filter(dd,Cluster==1) %>% select(PAGE) %>% group_by(PAGE) %>% count()
```

```{r}
# c) sort the pages by decreasing order of visits.
filter(dd,Cluster==1) %>% select(PAGE) %>% group_by(PAGE) %>% tally(sort=TRUE)
```

```{r}
# d) obtain the top 2 pages for recommendation.
filter(dd,Cluster==1) %>% select(PAGE) %>% group_by(PAGE) %>% tally(sort=TRUE) %>% top_n(2) %>% pull(PAGE)
```

4. Recommend the top 2 pages for users of cluster 2.

```{r}
filter(dd,Cluster==2) %>% select(PAGE) %>% group_by(PAGE) %>% tally(sort=TRUE) %>% top_n(2) %>% pull(PAGE)
```

5. Using the same clustering results, recommend the top 3 pages for user u2. From those top pages you should remove the pages that the user has already visited.

```{r}
# First, get the cluster of user2
cluster.u2 <-
dd %>% filter(USER=="u2") %>% select(Cluster) %>% head(1) %>% pull()
cluster.u2

# Second, get top3 pages from cluster for user2
rec.u2 <-
  filter(dd,Cluster==cluster.u2) %>% group_by(PAGE) %>% tally(sort=TRUE) %>% top_n(3) %>% select(PAGE)
rec.u2

# Third, get pages already visited by user2
seen.u2 <-
  dd %>% filter(USER=="u2") %>% select(PAGE)
seen.u2

# Finally, show what isn't in both groups
anti_join(rec.u2, seen.u2)
```

# 2.2 Recommendation using Association Rules

Load the package recommenderlab and read the log1.csv file (it is an expansion of log.csv with u7 and u8).

```{r}
# Preparations
library(recommenderlab)
library(readr)
log <- read_csv("~/4year/2semester/dtII/CSVs/log1.csv", col_types=list(col_factor(), col_factor()))
View(log)
```

6. Obtain a recommendation model using association rules with the first 6 users.

```{r}
# a) start by coercing the data frame with user-page access information from the log1.csv file to a binaryRatingMatrix (brm).
brm <- as(as.data.frame(log), "binaryRatingMatrix")
brm

# in order to check out what we have in the data frame
getData.frame(brm)
```

```{r}
# b) select the information on the first 6 users to be used as training offline data and save it to a new variable (e.g brm_offline).
brm_offline <- brm[1:6,]
```

```{r}
# c) inspect the content of brm_offline; use the function getRatingMatrix and getData.frame.
getData.frame(brm_offline)
getRatingMatrix(brm_offline)
# the best way lo 'look' at rating matrices
inspect(getRatingMatrix(brm_offline))
```

```{r}
# d) apply the functions rowCounts and colCounts to brm_offline; what information does it give you?
r <- rowCounts(brm_offline)
r
c <- colCounts(brm_offline)
c
```

```{r}
# e) apply the function image to brm_offline.
image(brm_offline)
```

```{r}
# f) obtain the recommender model based on association rules with the instruction: modelAR <- Recommender(brm_offline,"AR").
modelAR <- Recommender(brm_offline, "AR") # AR -> Association Rules
modelAR
```

```{r}
# g) apply the function getModel to the obtained model and then inspect the association rules that compose the model.
getModel(modelAR)

# generation of rules
rules <- getModel(modelAR)$rule_base
inspect(rules)
```

7. Suppose that u7 enters the system and becomes an active user. Deploy the recommendation model for him/her.

```{r}
# Getting old values of user 7
brm_u7 <- brm[7,]
# Checking the contents
getData.frame(brm_u7)
```

```{r}
# a) apply the predict function with the model and the rating matrix of the user, such that only the top 2 recommendations are given as output.
recsAR <- predict(modelAR, brm_u7, n=2)
recsAR
```

```{r}
# b) apply the function getList to the obtained predictions to inspect the actual recommendations; which are they?
getList(recsAR)
```

```{r}
# c) to comprove the obtained recommendations, filter the rules which have been triggered for this active user.
r <- subset(rules, lhs %in% c("C", "F"))
inspect(r)
```

8. Now suppose that u8 enters the system and becomes an active user. Deploy the recommendation model for him/her. Be critical regarding the results.

```{r}
brm_u8 <- brm[8,]
getData.frame(brm_u8)

recs8AR <- predict(modelAR, brm_u8, n=2)
recs8AR

getList(recs8AR)
```

9. Explore the types of recommendation models available for binary rating matrices.

```{r}
recommenderRegistry$get_entries(dataType="binaryRatingMatrix")
```

10. Make the top 2 recommendations to u7 and u8 using the popularity of the pages, instead of association rules. Try to understand the obtained recommendations.

```{r}
modelPop <- Recommender(brm_offline, "POPULAR")

recsPop <- predict(modelPop, brm[7:8,], n=2)
recsPop
getList(recsPop)
```

# 2.3 Recommendation using Collaborative Filtering

## Binary Rating Data

Considering the same binary rating matrix of the previous exercise brm_offline, build a recommendation model based on collaborative filtering.

11. Start by using the function similarity to build the similarity cosine matrix (only for first 6 users).

```{r}
# a) a user-based approach.
sCos_users <- similarity(brm_offline, method="cosine")
sCos_users
```

```{r}
# b) an item-based approach.
sCos_items <- similarity(brm_offline, method ="cosine", which="items")
sCos_items
```

12. Obtain the top 2 recommendations with user-based CF and item-based CF methods using the cosine similarity with a neighborhood of size 3, for:

```{r}
# model creation for user-based and item-based collaborative filtering
modelUBCF <- Recommender(brm_offline, 'UBCF', parameter=list(method="cosine" ,nn=3))
getModel(modelUBCF)

modelIBCF <- Recommender(brm_offline, 'IBCF', parameter=list(method="cosine" ,k=3))
getModel(modelIBCF)
```

```{r}
# a) active user u8
recsUBCF <- predict(modelUBCF, brm_u8, n=2)
getList(recsUBCF)

recsIBCF <- predict(modelIBCF, brm_u8, n=2)
getList(recsIBCF)
```

```{r}
# b) active user u7
recsUBCF <- predict(modelUBCF, brm_u7, n=2)
getList(recsUBCF)

recsIBCF <- predict(modelIBCF, brm_u7, n=2)
getList(recsIBCF)
```

## Non-Binary Rating Data

13. Explore the types of recommendation models available for real rating matrices

```{r}
recommenderRegistry$get_entries(dataType ="realRatingMatrix")
```

14. Read the file log1Ratings.csv, containing information on the ratings given to web pages by a set of users, into a data frame in R. Build and deploy the following collaborative filtering recommendation models using, again, the first 6 users for training:

```{r}
logR <- read_csv("~/4year/2semester/dtII/CSVs/log1Ratings.csv",
                      col_types=list(col_factor(),
                                     col_factor(),
                                     col_integer()))

rrm <- as(as.data.frame(logR), "realRatingMatrix")

getRatingMatrix(rrm)
image(rrm)

# using only first 6 users
rrm_offline <- rrm[1:6,]
getRatingMatrix(rrm_offline)
```

```{r}
# a) a user-based CF approach with two neighbors to predict the ratings of users u7 and u8

# model creation
modelUBCF_R <- Recommender(rrm_offline, 'UBCF', parameter=list(nn=2))
getModel(modelUBCF_R)

# applying model to user 7 and 8
recsUBCF_R <- predict(modelUBCF_R, rrm[7,], type="ratings")
getList(recsUBCF_R)

# user 8 suffers form cold-start(in R named numeric(0) is NA)
recsUBCF_R <- predict(modelUBCF_R, rrm[8,], type="ratings")
getList(recsUBCF_R)
```

```{r}
# b) an item-based CF approach with two neighbors to predict the ratings of users u7 and u8

# model creation
modelIBCF_R <- Recommender(rrm_offline, 'IBCF', parameter=list(k=2))
getModel(modelIBCF_R)

# applying model to user 7 and 8
recsIBCF_R <- predict(modelIBCF_R, rrm[7,], type="ratings")
getList(recsIBCF_R)

recsIBCF_R <- predict(modelIBCF_R, rrm[8,], type="ratings")
getList(recsIBCF_R)
```

# 2.4 Recommender Systems: Evaluation

15 Considering the log1 binary data, evaluate different recommendation strategies.

```{r}
log <- read_csv("~/4year/2semester/dtII/CSVs/log1.csv",
                      col_types=list(col_factor(),
                                     col_factor()))

brm <- as(as.data.frame(log), "binaryRatingMatrix")
```

```{r}
# a) Set the seed to 2021. Use the function evaluationScheme to define an evaluation scheme that splits the data into train and test set (80%-20% proportion) and establishes that 2 items of test cases are already known. In case one or more users do not comply with this setting, you can disregard them.
set.seed(2021) # for replication purposes
# error e <- evaluationScheme(brm, method="split", train=0.8, given=2)

# understanding the problem
rowCounts(brm)

# fix
brm <- brm[rowCounts(brm)>=2,]
e <- evaluationScheme(brm, method="split", train=0.8, given=2)
e
```

```{r}
# b) check how the data was split according to the previous evaluation scheme, using the function getData on the evaluation scheme with the argument’s "train", "known" and "unknown".
inspect(getRatingMatrix(brm))

inspect(getRatingMatrix(getData(e,"train")))
inspect(getRatingMatrix(getData(e,"known")))
inspect(getRatingMatrix(getData(e,"unknown")))
```

```{r}
# c) Define the list of methods that will be used to obtain the top N recommendations, as follows:

methods <- list(
    "popular" = list(name="POPULAR", param = NULL), 
    "user-based CF" = list(name="UBCF", param = NULL),
    "item-based CF" = list(name="IBCF", param = NULL)
)
```

```{r}
# d) Use the function evaluate with the previously defined evaluation scheme, methods and considering top 1, 3 and 5 recommendations for each of the models.
results <- evaluate(e, methods,
                    type="topNList", n=c(1,3,5))
```

```{r}
# e) Explore the obtained object.
avg(results)
```

```{r}
# f) Use the function getConfusionMatrix as one of the methods to obtain the corresponding confusion matrices. Be critical regarding the values that are shown.
getConfusionMatrix(results[["popular"]])

model1 <- Recommender(getData(e,"train"), "POPULAR")
preds1 <- predict(model1, getData(e,"known"), n=3)
getList(preds1)
```

```{r}
# g) Plot the ROC curves for each of the methods and different values of N. What can you conclude?
plot(results, annotate="TRUE")
```

```{r}
# h) Plot the precision/recall curves for each of the methods and different values of N. What can you conclude?
plot(results, "prec/rec", annotate=TRUE)
```
